Hydras \& Co.

### 2023-07-15 doc/chapter-natural-deduction.tex
work on chapter-natural-deduction

Let us keep in mind that the derived connectives: \texttt{orH}, \texttt{andH}, etc. and the existential quantifier \texttt{existH}  are defined
in terms of \texttt{impH}, \texttt{notH}, \texttt{forallH}.
By unfolding these definitions, we prove easily a few natural deduction rules for the derived symbols. 
For instance, the law of excluded middle for $f$: $ T\sdash \sim f \vee f$
for any $T$,  is just an abbreviation of $T \sdash \sim\sim f \arrow f$.

@@

@@

>>>>

Let us keep in mind that the derived connectives: \texttt{orH}, \texttt{andH}, etc. and the existential quantifier \texttt{existH}  are defined
in terms of \texttt{impH}, \texttt{notH}, \texttt{forallH}.
By unfolding these definitions, we prove easily a few natural deduction rules for the derived symbols. 
For instance, the law of excluded middle for $f$: $ T\sdash \sim f \vee f$
for any $T$,  is just an abbreviation of $T \sdash \sim\sim{}f \arrow f$.

@@

\begin{remark}
  The lines marked ``optional'' are just here in order to
temporarily deactivate the notation which print any formula 
of the form $\sim{}\!A \arrow B$ as \texttt{$A$ \disj' $B$}.
 These three lines can be safely removed.
\end{remark}

Let us go on \dots. We leave the completion of the proofs as an exercise. We encourage the reader to write h.er.is own proofs, then compare them with the scripts of \href{../theories/html/hydras.Ackermann.folLogic.html}{folLogic}.

@@

\inputsnippets{folLogic/orE}

\inputsnippets{folLogic/orSys}
